/section{MyoBand arm}
%What does the band consist of?
%Electrodes, gyroscope and accelerometer
%Build-in filters and stuff like that?
%Sampling frequency

Myo band arm is a gesture interactive system developed by Thalmic Labs capable of indentifying the movement of hand and arms  to be able to interact and control different electronic devices. 
%imagen de myoband arm(negro)%


This wearable physical device (arm band positioned in the upper forearm ) counts with eight medical grade stainless steel electromyogram (EMG) sensors, resposible to recognize and performe each gesture. The systems counts with sizing clips which allow for a more tight grip, more appropriate for smaller arms. 

In addition has nine axis inertial measurement unit(IMU) which enables the detection of arm movement. IMU include three axis gyroscope,three axis accelerometter and three axis magnetometer.

Offers five pre-defined gestures to date as showed in the image. Provides haptic feedback through short, medium or long vibrations to correct moves or activate the system.

The Myo armband is capable of pulling sEMG data at a sample rate of 200Hz.
The remaining data accelerometer,gyroscoe and magnetometer 50HZ

%/begin{figure}
%poner imagen del los gestos%
%/end{figure}

%How does it communicate with the computer?
%Connection
%Programs that can be used to interface with the arm
%What kind of data will be received from the myo band?

data of hand gestures can be sent to other systems using Bluetooth links
MYB Recorded signals were sent via Bluetooth 4.0 

It's compatible with several devices and software %(revisar)
it is equipped with an ARM Cortex-M4 microprocessor of low consumption

usb chargin port
logo led
status led

spatial data 
gestural data
%it connecrs to a PC or tablet via bluetooth Low Energy and allows both raw data streaming and the use of a proprietary library for gesture recognition.The signal processing is performed on the host platform and the used algorithms are not documented (poner de otra manera)


/